Exploring ISD(S)1 Data

### 2021-08-02 exploring_isds1_data.Rmd
saved one of the graphs for hospital beds data

@@

```{r}
isds1 %>% count(health_board)

@@

## occupancy plot
isds1 %>% 
  filter(!is.na(location_name)) %>%
  filter(year %in% 2015:2021) %>%
  filter(specialty_description == "Palliative Medicine") %>%
  ggplot(data = .) +
  geom_point(aes(x = Quarter, y = PercentageOccupancy, group = location_name, colour = location_name), position = position_dodge()) +
  geom_line(aes(x = Quarter, y = PercentageOccupancy, group = location_name, colour = location_name)) +
  facet_wrap(health_board ~ .) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45))

## total beds occupied
isds1 %>% 
  filter(!is.na(location_name)) %>%
  filter(year %in% 2015:2021) %>%
  filter(specialty_description == "Palliative Medicine") %>%
  ggplot(data = .) +
  geom_point(aes(x = Quarter, y = TotalOccupiedBeds, group = location_name, colour = location_name), position = position_dodge()) +
  geom_line(aes(x = Quarter, y = TotalOccupiedBeds, group = location_name, colour = location_name)) +
  facet_wrap(health_board ~ .) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45))

## available beds (all beds - total occ.)
isds1 %>% 
  filter(!is.na(location_name)) %>%
  filter(year %in% 2015:2021) %>%
  filter(specialty_description == "Palliative Medicine") %>%
  ggplot(data = .) +
  geom_point(aes(x = Quarter, y = AvailableBeds, group = location_name, colour = location_name), position = position_dodge()) +
  geom_line(aes(x = Quarter, y = AvailableBeds, group = location_name, colour = location_name)) +
  facet_wrap(health_board ~ .) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45))
```

>>>>

An alternative location for downloading [hospital bed data is here](https://publichealthscotland.scot/media/7634/beds-by-nhs-board-of-treatment-and-specialty-to-december-2020.csv). This appears to be somewhat more neatly formatted and ready for analysis.

@@

```{r}
if (!dir.exists("./isd(s)1_exploration")) dir.create("./isd(s)1_exploration")

isds1 %>% count(health_board)

@@

## occupancy plot
(occupancy_2020_palliative_specialty_hospitals <-
  isds1 %>% 
  filter(!is.na(location_name)) %>%
  filter(year %in% 2015:2021) %>%
  filter(specialty_description == "Palliative Medicine") %>%
  ggplot(data = .) +
  geom_point(aes(x = Quarter, y = PercentageOccupancy, group = location_name, colour = location_name), position = position_dodge(width = 0.5)) +
  geom_line(aes(x = Quarter, y = PercentageOccupancy, group = location_name, colour = location_name), position = position_dodge(width = 0.5)) +
  annotate(geom = "rect", xmin = "2020Q2", xmax = "2020Q4", ymin = -Inf, ymax = Inf, fill = "grey90", alpha = 0.4) +
  facet_wrap(health_board ~ .) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 80, vjust = 0))
  )
occupancy_2020_palliative_specialty_hospitals %>%
  ggsave(plot = ., filename = "./isd(s)1_exploration/occupancy_2020_palliative_specialty_hospitals.png", width = 15, height = 6, dpi = 300)

## total beds occupied
isds1 %>% 
  filter(!is.na(location_name)) %>%
  filter(year %in% 2015:2021) %>%
  filter(specialty_description == "Palliative Medicine") %>%
  ggplot(data = .) +
  geom_point(aes(x = Quarter, y = TotalOccupiedBeds, group = location_name, colour = location_name), position = position_dodge(width = 0.5)) +
  geom_line(aes(x = Quarter, y = TotalOccupiedBeds, group = location_name, colour = location_name), position = position_dodge(width = 0.5)) +
  annotate(geom = "rect", xmin = "2020Q2", xmax = "2020Q4", ymin = -Inf, ymax = Inf, fill = "grey90", alpha = 0.4) +
  facet_wrap(health_board ~ .) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45))

## available beds (all beds - total occ.)
isds1 %>% 
  filter(!is.na(location_name)) %>%
  filter(year %in% 2015:2021) %>%
  filter(specialty_description == "Palliative Medicine") %>%
  ggplot(data = .) +
  geom_point(aes(x = Quarter, y = AvailableBeds, group = location_name, colour = location_name), position = position_dodge(width = 0.5)) +
  geom_line(aes(x = Quarter, y = AvailableBeds, group = location_name, colour = location_name), position = position_dodge(width = 0.5)) +
  annotate(geom = "rect", xmin = "2020Q2", xmax = "2020Q4", ymin = -Inf, ymax = Inf, fill = "grey90", alpha = 0.4) +
  facet_wrap(health_board ~ .) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45))
```
